Manuscript_rsfMRI

### 2020-10-26 draft_rsfmri.Rmd
added absolute path import

```{r "Package loading", include=FALSE}
library(plyr)
library(dplyr)
library(tidyr)
library(knitr)
library(kableExtra)
library(haven)
library(psych)
library(patchwork)
library(lsr) 
library(wesanderson)
library(cowplot)
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, fig.height=2, fig.width=4)
options(knitr.table.format = "latex") 
# put the path to this file here (working directory for Rmarkdown):
opts_knit$set(root.dir = "/data/pt_02161/Publications/Papers/manuscript_rsfmri/")
```
\newpage
# Abstract

@@

```{r Load data, include=FALSE}
source("/data/pt_02161/Analysis/Project2_resting_state/seed-based/Second_level /adi_analysis/get_subject_ID_group_tp_forSwE.R")
final = save_txt_for_swe(IG_only = FALSE, only2tp = FALSE)
opts_knit$set(root.dir = "/data/pt_02161/Publications/Papers/manuscript_rsfmri/")

@@

dfw <- tidyr::pivot_wider(data = final,
                          id_cols = c("subj.ID","condition","Sex","Age_BL"),
                          names_from = "tp",
                          values_from = c("BMI","logmFD")
)
```

>>>>

```{r "Package loading", include=FALSE}
library(plyr)
library(dplyr)
library(tidyr)
library(knitr)
library(kableExtra)
library(haven)
library(psych)
library(patchwork)
library(lsr) 
library(wesanderson)
library(cowplot)
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, fig.height=2, fig.width=4)
options(knitr.table.format = "latex") 
# put the path to this file here (working directory for Rmarkdown):
opts_knit$set(root.dir = getwd())
```
\newpage
# Abstract

@@

```{r Load data, include=FALSE}
source("get_subject_ID_group_tp_forSwE.R")
final = save_txt_for_swe(IG_only = FALSE, only2tp = FALSE)

@@

dfw <- tidyr::pivot_wider(data = final,
                          id_cols = c("subj.ID","condition","Sex","Age_BL"),
                          names_from = "tp",
                          values_from = c("BMI","logmFD"))
```
